---
title: "B_Context_Stats"
author: "Emilio Robleda"
date: "`r Sys.Date()`"
output: html_document
---
## Load libraries data

```{r load libraries message=FALSE, warning=FALSE}
library(tidyverse)
library(lubridate)
library(rvg)
library(ggrepel)
library(paletteer)
library(quanteda)
library(quanteda.corpora)
library(quanteda.dictionaries)
library(quanteda.sentiment)
library(quanteda.textmodels)
library(quanteda.textplots)
library(quanteda.textstats)
library(openxlsx)

```

```{r load data}
# Unzip folder and load data
zip_folder <- "data.zip"
file_to_extract <- "data.csv"
destination_path <- "./"  # Specify the desired destination path

unzip(zip_folder, files = file_to_extract, exdir = destination_path)
data <- read_csv("data.csv")

```
```{r}
str(data)

```


## Data manipulation

Change the format of date variables and include new variables

```{r dates in format}
# Create a new variable called "comment_date"
data$comment_date <- as.Date(data$date, format = "%m/%d/%Y", na.rm = TRUE)
data$comment_date[is.na(data$comment_date)] <- as.Date(data$date[is.na(data$comment_date)])
# Convert "post_date" variable to date format (DD/MM/YYYY)
data$posts_date <- as.Date(data$post_date, format = "%m/%d/%Y", na.rm = TRUE)
data$posts_date[is.na(data$posts_date)] <- as.Date(data$post_date[is.na(data$posts_date)])
```


```{r create new variables}
data <- data %>%
  mutate(
    # Dummy to see if comment was deleted
    deleted = ifelse(comment == "[deleted]", 1, 0),
    # Dummy to see if comment was deleted
    removed = ifelse(comment == "[removed]", 1, 0),
    # Dummy to see if comment was deleted or removed
    deleted_removed = ifelse(deleted == 1 | removed == 1, 1, 0),
    # Dummy to see if the AutoMod was the author of a comment
    automod = ifelse(author == "AutoModerator", 1, 0),
    # Dummy to see if the post was submit during the Euro 2022 (for this research, in July 2022)
    during_euros = ifelse(posts_date >= as.Date("2022-07-01") & posts_date < as.Date("2022-08-01"), 1, 0),
    # Dummy to see if the post was submitted after the Euro 2022 (Aug-2022 onwards)
    after_euros = ifelse(posts_date >= as.Date("2022-08-01"), 1, 0),
    # Treatment group is one of those four subreddits (their teams had a player in England's Euro 2022 squad) 
    treatment = ifelse(subreddit %in% c("reddevils", "chelseafc", "Gunners", "MCFC"), 1, 0),
    # Have a dummy of only one observation per unique post (to calculate avg_post_score later)
    first_comment = ifelse(duplicated(post_timestamp), 0, 1),
    # Calculate the length in terms of characters (NOT TOKENS) per comment
    comment_chars = ifelse(deleted == 1 | removed == 1 | automod == 1, NA, nchar(comment)),
    # Create a month 
    month_year = paste(year(posts_date), month(posts_date), sep = "-"),
    # Create a subreddit_month character variable
    subreddit_month = paste(subreddit, month_year, sep = "_"))

data <- data %>%
  # Group by unique posts
  group_by(post_timestamp) %>%
  # Create a dummy to know whether the post's thread had at least one deleted or removed comment
  mutate(moderated_post = ifelse(first_comment == 1 & any(deleted_removed == 1), 1, 0)) %>%
  # Ungroup data
  ungroup()

```


```{r filter until May 2023}
# Filter observations to remove June 2023 observations
data <- data %>%
  filter(posts_date < "2023-06-01")

```

## Descriptive plots

Build database for descriptive plots

```{r create df}
n_distinct(data$post_timestamp)
nrow(data)

posts_data <- data %>%
  group_by(month_year) %>%
  summarise(post = n_distinct(post_timestamp),
            comments = n_distinct(timestamp),
            post_score = mean(post_score),
            chars = mean(comment_chars, na.rm = T),
            avg_com = comments/post)  %>%
  mutate(month_year = as.Date(paste0(month_year, "-01"), format = "%Y-%m-%d"))

sum(posts_data$post)
sum(posts_data$comments)
posts_data$year <- format(posts_data$month_year, "%Y")

average_post_score_per_year <- posts_data %>%
  group_by(year) %>%
  summarize(avg_post_score = mean(post_score, na.rm = TRUE))
average_post_score_per_year
average_comments_per_year <- posts_data %>%
  group_by(year) %>%
  summarize(avg_comments = mean(avg_com, na.rm = TRUE))
average_post_score_per_year
average_comments_per_year

```

Create and Print Descriptive Plots

```{r create plots}
# Month Analysis
posts_plot <- ggplot(posts_data, aes(x = month_year, y = post)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Women's Football Related Posts",
       subtitle = "Data limited to 17 subreddits",
       x = "Year",
       y = "Posts per month") +
  scale_x_date(date_breaks = "2 year", date_labels = "%Y") +
  theme_minimal()

posts_plot

# Month Analysis
comments_plot <- ggplot(posts_data, aes(x = month_year, y = comments)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Comments in Women's Football Related Posts Threads",
       subtitle = "Data limited to 17 subreddits",
       x = "Year",
       y = "Comments per Month") +
  scale_x_date(date_breaks = "2 year", date_labels = "%Y") +
  theme_minimal()

comments_plot

# Month Analysis
avg_com_plot <- ggplot(posts_data, aes(x = month_year, y = avg_com)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Comments per Post Regarding Women's Football Related Posts",
       subtitle = "Data limited to 17 subreddits",
       x = "Year",
       y = "Avg. Comments per Post per Month") +
  scale_x_date(date_breaks = "2 year", date_labels = "%Y") +
  theme_minimal()

avg_com_plot

# Month Analysis
pscore_plot <- ggplot(posts_data, aes(x = month_year, y = post_score)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Average Post Score Regarding Women's Football Related Posts",
       subtitle = "Data limited to 17 subreddits",
       x = "Year",
       y = "Average Post Score per Month") +
  scale_x_date(date_breaks = "2 year", date_labels = "%Y") +
  theme_minimal()

pscore_plot

# Month Analysis
chars_plot <- ggplot(posts_data, aes(x = month_year, y = chars)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Average Characters per Comment Regarding Women's Football Related Posts",
       subtitle = "Data limited to 17 subreddits",
       x = "Year",
       y = "verage Characters per Comment per month") +
  scale_x_date(date_breaks = "2 year", date_labels = "%Y") +
  theme_minimal()

chars_plot

```

## Network Analysis: authors and posts

### Build database for Network Analysis

```{r create first df}
subreddit_authors <- data %>%
  group_by(subreddit, month_year) %>%
  summarise(distinct_authors = n_distinct(post_author),
            total_posts = n_distinct(post_timestamp),
            .groups = "drop") %>%
  mutate(month = as.Date(paste0(month_year, "-01"), format = "%Y-%m-%d"))

```

### Unique Post Authors per Month per Subreddit 

```{r create first plot, fig.height=15, fig.width=10}
authors_p1 <- ggplot(subreddit_authors) +
 aes(x = month, y = distinct_authors) +
 geom_point(shape = "circle", size = 1, 
 colour = "#112446") +
 labs(title = "Distinct Post Authors per Month",
      subtitle = "Women's Football Related Posts for 17 subreddits",
      x = "Different Authors per Month",
      y = "Date") +
 theme_minimal() +
 facet_wrap(vars(subreddit), ncol = 3, scales = "free_y") +
 scale_y_continuous(breaks = seq(min(subreddit_authors$distinct_authors),
                                 max(subreddit_authors$distinct_authors), by = 2)) +
 scale_x_date(date_breaks = "2 year", date_labels = "%Y") +
  theme(panel.grid = element_blank())
authors_p1

```
### Cumulative Sum of Posts and Unique Authors per Subreddit

```{r create second df}
pauthor_cumsum <- data %>%
  mutate(month = as.Date(paste0(month_year, "-01"), format = "%Y-%m-%d")) %>%
  group_by(subreddit) %>%
  arrange(month) %>%
  mutate(cumsum_pauthor = cumsum(!duplicated(post_author))) %>%
  mutate(cumsum_posts = cumsum(!duplicated(post_timestamp))) %>%
  distinct(post_title, .keep_all = TRUE) %>%
  group_by(post_author) %>%
  mutate(author_count = n_distinct(post_timestamp)) %>%
  ungroup() %>%
  select(post_author, month, subreddit, post_timestamp, post_title, cumsum_pauthor, cumsum_posts, author_count)

```

```{r create plots, fig.height=8, fig.width=12}
max_x <- pauthor_cumsum %>%
  group_by(subreddit) %>%
  summarise(max_x = max(month),
            cumsum_posts = last(cumsum_posts))

authors_p2 <- ggplot(pauthor_cumsum) +
  aes(x = month, y = cumsum_posts, color = subreddit) +
  geom_point(shape = "circle", size = 1) +
  geom_text_repel(data = max_x, aes(x = max_x, y = cumsum_posts,
                                    label = paste(subreddit, cumsum_posts, sep = " "),
                                    color = subreddit),
                  hjust = 1, vjust = 1, size = 4.5) +
  labs(title = "Cumulative Sum of Posts per Subreddit",
       subtitle = "Women's Football Related Posts",
       x = "Year",
       y = "Cumulative Sum of Posts") +
  theme_minimal() +
  scale_y_continuous(breaks = seq(0, max(pauthor_cumsum$cumsum_posts), by = 25)) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  scale_color_manual(values = paletteer_d("ggsci::default_ucscgb")) +
  theme(panel.grid.major.x = element_line(colour = "grey50", linetype = "dashed"),
        legend.position = "none",
        panel.grid.minor.y = element_blank())

authors_p2

```

```{r more plots, fig.height=8, fig.width=12}
max_x <- pauthor_cumsum %>%
  group_by(subreddit) %>%
  summarise(max_x = max(month),
            cumsum_pauthor = last(cumsum_pauthor))

authors_p3 <- ggplot(pauthor_cumsum) +
  aes(x = month, y = cumsum_pauthor, color = subreddit) +
  geom_point(shape = "circle", size = 1) +
  geom_text_repel(data = max_x, aes(x = max_x, y = cumsum_pauthor,
                                    label = paste(subreddit, cumsum_pauthor, sep = " "),
                                    color = subreddit),
                  hjust = 1, vjust = 1, size = 4.5) +
  labs(title = "Cumulative Sum of Different Post Authors per Subreddit",
       subtitle = "Women's Football Related Posts",
       caption = "Post Authors may repeat across subreddits",
       x = "Year",
       y = "Cumulative Sum of Unique Post Authors per Subreddit") +
  theme_minimal() +
  scale_y_continuous(breaks = seq(0, max(pauthor_cumsum$cumsum_pauthor), by = 25)) +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  scale_color_manual(values = paletteer_d("ggsci::default_ucscgb")) +
  theme(panel.grid.major.x = element_line(colour = "grey50", linetype = "dashed"),
        legend.position = "none",
        panel.grid.minor.y = element_blank())

authors_p3

```

### Main Authors in terms of Women's Football

```{r table of authors}
# Create the new dataframe ordered by author_count and select the desired variables
authors_table <- pauthor_cumsum %>%
  group_by(post_author) %>%
  summarise(
    posts = first(author_count),
    subreddit_name = first(subreddit),
    subreddits = n_distinct(subreddit)
  ) %>%
  arrange(desc(posts)) %>%
  mutate(
    ranking = row_number(),
    subreddit_name = ifelse(subreddits > 1, "Multiple subreddits", subreddit_name)) %>%
  select(ranking, post_author, posts, subreddits, subreddit_name)

# View the resulting dataframe
authors_table

write.xlsx(authors_table, file = "authors_data.xlsx")

total_posts <- sum(authors_table$posts)
total_authors <- nrow(authors_table)

```

## Natural Language Processing

```{r build dfm}
# Create a corpus
comments_corpus <- corpus(data$comment)
# Tokenize the corpus
comments_tokens <- tokens(comments_corpus,
                   remove_punct = T,
                   remove_symbols = T,
                   remove_numbers = T,
                   remove_url = T) %>%
  tokens_tolower() %>%
  tokens_remove(c(stopwords("english"), "also", "s", "t", "m", "get", "go", "can", "gt", "just")) %>%
  tokens_wordstem()
# Include docvars
docvars(comments_tokens, c(names(data)[-which(names(data) == "comment")])) <- data[, -which(names(data) == "comment")]
# Convert tokenized corpus into a dfm
comments_dfm <- dfm(comments_tokens)

comments_dfm

```

```{r display wordclouds}
# Create a subset dfm based on the conditions
###sub_g0_t0 <- dfm_subset(comments_dfm, treatment == 0 & after_euros == 0)
###sub_g1_t0 <- dfm_subset(comments_dfm, treatment == 1 & after_euros == 0)
###sub_g0_t1 <- dfm_subset(comments_dfm, treatment == 0 & after_euros == 1)
###sub_g1_t1 <- dfm_subset(comments_dfm, treatment == 1 & after_euros == 1)

# Create wordcloud plot using the subset dfm
###textplot_wordcloud(sub_g0_t0, rotation = 0, min_size = 0.75, max_size = 3, max_words = 50)
###textplot_wordcloud(sub_g1_t0, rotation = 0, min_size = 0.75, max_size = 3, max_words = 50)
###textplot_wordcloud(sub_g0_t1, rotation = 0, min_size = 0.75, max_size = 3, max_words = 50)
###textplot_wordcloud(sub_g1_t1, rotation = 0, min_size = 0.75, max_size = 3, max_words = 50)

```

```{r generate bigrams}
###comments_tokens_bi <- tokens_ngrams(comments_tokens, n=2)
###comments_dfm_bi <- dfm(comments_tokens_bi)

###comments_dfm_bi

###textstat_frequency(comments_dfm_bi, 30, groups = subreddit)
textstat_frequency(comments_dfm, 100)

```

```{r build month word freqs}
month_year_freq <- textstat_frequency(comments_dfm, 50, groups = month_year)
month_year_freq$month_year <- ym(month_year_freq$group) 
month_year_freq <- month_year_freq %>%
  select(-group)
month_year_freq
```

### Select specific words
```{r select specific words}
women_freq <- month_year_freq %>%
  filter(feature == "women") %>%
  rename(women_docfreq = docfreq)
men_freq <- month_year_freq %>%
  filter(feature == "men") %>%
  rename(men_docfreq = docfreq)
game_freq <- month_year_freq %>%
  filter(feature == "game") %>%
  rename(game_docfreq = docfreq)
ladi_freq <- month_year_freq %>%
  filter(feature == "ladi") %>%
  rename(ladi_docfreq = docfreq)
player_freq <- month_year_freq %>%
  filter(feature == "player") %>%
  rename(player_docfreq = docfreq)
match_freq <- month_year_freq %>%
  filter(feature == "match") %>%
  rename(match_docfreq = docfreq)
win_freq <- month_year_freq %>%
  filter(feature == "win") %>%
  rename(win_docfreq = docfreq)
hope_freq <- month_year_freq %>%
  filter(feature == "hope") %>%
  rename(hope_docfreq = docfreq)
season_freq <- month_year_freq %>%
  filter(feature == "season") %>%
  rename(season_docfreq = docfreq)
goal_freq <- month_year_freq %>%
  filter(feature == "goal") %>%
  rename(goal_docfreq = docfreq)
team_freq <- month_year_freq %>%
  filter(feature == "team") %>%
  rename(team_docfreq = docfreq)
club_freq <- month_year_freq %>%
  filter(feature == "club") %>%
  rename(club_docfreq = docfreq)
footbal_freq <- month_year_freq %>%
  filter(feature == "footbal") %>%
  rename(footbal_docfreq = docfreq)
leagu_freq <- month_year_freq %>%
  filter(feature == "leagu") %>%
  rename(leagu_docfreq = docfreq)
play_freq <- month_year_freq %>%
  filter(feature == "play") %>%
  rename(play_docfreq = docfreq)

```

```{r join in one df}
# Join the data frames by month_year, keeping comment and docfreq columns
monthly_docfreqs <- left_join(posts_data, women_freq %>% 
                                select(month_year, women_docfreq),
                              by = "month_year") %>%
  left_join(men_freq %>% select(month_year, men_docfreq),
                              by = "month_year") %>%
  left_join(game_freq %>% select(month_year, game_docfreq),
                              by = "month_year") %>%
  left_join(ladi_freq %>% select(month_year, ladi_docfreq),
                              by = "month_year") %>%
  left_join(player_freq %>% select(month_year, player_docfreq),
                              by = "month_year") %>%
  left_join(match_freq %>% select(month_year, match_docfreq),
                              by = "month_year") %>%
  left_join(win_freq %>% select(month_year, win_docfreq),
                              by = "month_year") %>%
  left_join(hope_freq %>% select(month_year, hope_docfreq),
                              by = "month_year") %>%
  left_join(season_freq %>% select(month_year, season_docfreq),
                              by = "month_year") %>%
  left_join(goal_freq %>% select(month_year, goal_docfreq),
                              by = "month_year") %>%
  left_join(team_freq %>% select(month_year, team_docfreq),
                              by = "month_year") %>%
  left_join(club_freq %>% select(month_year, club_docfreq),
                              by = "month_year") %>%
  left_join(footbal_freq %>% select(month_year, footbal_docfreq),
                              by = "month_year") %>%
  left_join(leagu_freq %>% select(month_year, leagu_docfreq),
                              by = "month_year") %>%
  left_join(play_freq %>% select(month_year, play_docfreq),
                              by = "month_year") %>%
  select(month_year, comments,
         women_docfreq, men_docfreq, game_docfreq, ladi_docfreq, player_docfreq,
         match_docfreq, win_docfreq, hope_docfreq, season_docfreq, goal_docfreq,
         team_docfreq, club_docfreq, footbal_docfreq, leagu_docfreq, play_docfreq) %>%
  mutate(women_docfreq = ifelse(is.na(women_docfreq), 0, women_docfreq),
         women_ratio = round((women_docfreq / comments) * 100, 2),
         men_docfreq = ifelse(is.na(men_docfreq), 0, men_docfreq),
         men_ratio = round((men_docfreq / comments) * 100, 2),
         game_docfreq = ifelse(is.na(game_docfreq), 0, game_docfreq),
         game_ratio = round((game_docfreq / comments) * 100, 2),
         ladi_docfreq = ifelse(is.na(ladi_docfreq), 0, ladi_docfreq),
         ladi_ratio = round((ladi_docfreq / comments) * 100, 2),
         player_docfreq = ifelse(is.na(player_docfreq), 0, player_docfreq),
         player_ratio = round((player_docfreq / comments) * 100, 2),
         match_docfreq = ifelse(is.na(match_docfreq), 0, match_docfreq),
         match_ratio = round((match_docfreq / comments) * 100, 2),
         win_docfreq = ifelse(is.na(win_docfreq), 0, win_docfreq),
         win_ratio = round((win_docfreq / comments) * 100, 2),
         hope_docfreq = ifelse(is.na(hope_docfreq), 0, hope_docfreq),
         hope_ratio = round((hope_docfreq / comments) * 100, 2),
         season_docfreq = ifelse(is.na(season_docfreq), 0, season_docfreq),
         season_ratio = round((season_docfreq / comments) * 100, 2),
         goal_docfreq = ifelse(is.na(goal_docfreq), 0, goal_docfreq),
         goal_ratio = round((goal_docfreq / comments) * 100, 2),
         team_docfreq = ifelse(is.na(team_docfreq), 0, team_docfreq),
         team_ratio = round((team_docfreq / comments) * 100, 2),
         club_docfreq = ifelse(is.na(club_docfreq), 0, club_docfreq),
         club_ratio = round((club_docfreq / comments) * 100, 2),
         footbal_docfreq = ifelse(is.na(footbal_docfreq), 0, footbal_docfreq),
         footbal_ratio = round((footbal_docfreq / comments) * 100, 2),
         leagu_docfreq = ifelse(is.na(leagu_docfreq), 0, leagu_docfreq),
         leagu_ratio = round((leagu_docfreq / comments) * 100, 2),
         play_docfreq = ifelse(is.na(play_docfreq), 0, play_docfreq),
         play_ratio = round((play_docfreq / comments) * 100, 2)) %>%
  arrange(month_year) %>%
  filter(month_year >= "2017-01-01")

monthly_docfreqs

```

```{r plot word use in time}
# Month Analysis
women_freqplot <- ggplot(monthly_docfreqs, aes(x = month_year, y = women_ratio)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Comments that Included the Stem 'WOMEN' per Month",
       subtitle = "Comments inside Women's football posts from 17 selected subreddits",
       caption = "Data from Jan17-May23 where min comments was 30 in Feb-2017",
       x = "Year",
       y = "Share of comments including the stemmed word") +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  theme_minimal()
women_freqplot

# Month Analysis
men_freqplot <- ggplot(monthly_docfreqs, aes(x = month_year, y = men_ratio)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Comments that Included the Stem 'MEN' per Month",
       subtitle = "Comments inside Women's football posts from 17 selected subreddits",
       caption = "Data from Jan17-May23 where min comments was 30 in Feb-2017",
       x = "Year",
       y = "Share of comments including the stemmed word") +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  theme_minimal()
men_freqplot

# Month Analysis
game_freqplot <- ggplot(monthly_docfreqs, aes(x = month_year, y = game_ratio)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Comments that Included the Stem 'GAME' per Month",
       subtitle = "Comments inside Women's football posts from 17 selected subreddits",
       caption = "Data from Jan17-May23 where min comments was 30 in Feb-2017",
       x = "Year",
       y = "Share of comments including the stemmed word") +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  theme_minimal()
game_freqplot

# Month Analysis
ladi_freqplot <- ggplot(monthly_docfreqs, aes(x = month_year, y = ladi_ratio)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Comments that Included the Stem 'LADI' per Month",
       subtitle = "Comments inside Women's football posts from 17 selected subreddits",
       caption = "Data from Jan17-May23 where min comments was 30 in Feb-2017",
       x = "Year",
       y = "Share of comments including the stemmed word") +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  theme_minimal()
ladi_freqplot

# Month Analysis
player_freqplot <- ggplot(monthly_docfreqs, aes(x = month_year, y = player_ratio)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Comments that Included the Stem 'PLAYER' per Month",
       subtitle = "Comments inside Women's football posts from 17 selected subreddits",
       caption = "Data from Jan17-May23 where min comments was 30 in Feb-2017",
       x = "Year",
       y = "Share of comments including the stemmed word") +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  theme_minimal()
player_freqplot

# Month Analysis
match_freqplot <- ggplot(monthly_docfreqs, aes(x = month_year, y = match_ratio)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Comments that Included the Stem 'MATCH' per Month",
       subtitle = "Comments inside Women's football posts from 17 selected subreddits",
       caption = "Data from Jan17-May23 where min comments was 30 in Feb-2017",
       x = "Year",
       y = "Share of comments including the stemmed word") +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  theme_minimal()
match_freqplot

# Month Analysis
win_freqplot <- ggplot(monthly_docfreqs, aes(x = month_year, y = win_ratio)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Comments that Included the Stem 'WIN' per Month",
       subtitle = "Comments inside Women's football posts from 17 selected subreddits",
       caption = "Data from Jan17-May23 where min comments was 30 in Feb-2017",
       x = "Year",
       y = "Share of comments including the stemmed word") +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  theme_minimal()
win_freqplot

# Month Analysis
hope_freqplot <- ggplot(monthly_docfreqs, aes(x = month_year, y = hope_ratio)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Comments that Included the Stem 'HOPE' per Month",
       subtitle = "Comments inside Women's football posts from 17 selected subreddits",
       caption = "Data from Jan17-May23 where min comments was 30 in Feb-2017",
       x = "Year",
       y = "Share of comments including the stemmed word") +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  theme_minimal()
hope_freqplot

# Month Analysis
season_freqplot <- ggplot(monthly_docfreqs, aes(x = month_year, y = season_ratio)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Comments that Included the Stem 'SEASON' per Month",
       subtitle = "Comments inside Women's football posts from 17 selected subreddits",
       caption = "Data from Jan17-May23 where min comments was 30 in Feb-2017",
       x = "Year",
       y = "Share of comments including the stemmed word") +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  theme_minimal()
season_freqplot

# Month Analysis
goal_freqplot <- ggplot(monthly_docfreqs, aes(x = month_year, y = goal_ratio)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Comments that Included the Stem 'GOAL' per Month",
       subtitle = "Comments inside Women's football posts from 17 selected subreddits",
       caption = "Data from Jan17-May23 where min comments was 30 in Feb-2017",
       x = "Year",
       y = "Share of comments including the stemmed word") +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  theme_minimal()
goal_freqplot

# Month Analysis
team_freqplot <- ggplot(monthly_docfreqs, aes(x = month_year, y = team_ratio)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Comments that Included the Stem 'TEAM' per Month",
       subtitle = "Comments inside Women's football posts from 17 selected subreddits",
       caption = "Data from Jan17-May23 where min comments was 30 in Feb-2017",
       x = "Year",
       y = "Share of comments including the stemmed word") +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  theme_minimal()
team_freqplot

# Month Analysis
club_freqplot <- ggplot(monthly_docfreqs, aes(x = month_year, y = club_ratio)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Comments that Included the Stem 'CLUB' per Month",
       subtitle = "Comments inside Women's football posts from 17 selected subreddits",
       caption = "Data from Jan17-May23 where min comments was 30 in Feb-2017",
       x = "Year",
       y = "Share of comments including the stemmed word") +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  theme_minimal()
club_freqplot

# Month Analysis
footbal_freqplot <- ggplot(monthly_docfreqs, aes(x = month_year, y = footbal_ratio)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Comments that Included the Stem 'FOOTBAL' per Month",
       subtitle = "Comments inside Women's football posts from 17 selected subreddits",
       caption = "Data from Jan17-May23 where min comments was 30 in Feb-2017",
       x = "Year",
       y = "Share of comments including the stemmed word") +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  theme_minimal()
footbal_freqplot

# Month Analysis
leagu_freqplot <- ggplot(monthly_docfreqs, aes(x = month_year, y = leagu_ratio)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Comments that Included the Stem 'LEAGU' per Month",
       subtitle = "Comments inside Women's football posts from 17 selected subreddits",
       caption = "Data from Jan17-May23 where min comments was 30 in Feb-2017",
       x = "Year",
       y = "Share of comments including the stemmed word") +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  theme_minimal()
leagu_freqplot

# Month Analysis
play_freqplot <- ggplot(monthly_docfreqs, aes(x = month_year, y = play_ratio)) +
  geom_point() +
  geom_smooth() +
  labs(title = "Comments that Included the Stem 'PLAY' per Month",
       subtitle = "Comments inside Women's football posts from 17 selected subreddits",
       caption = "Data from Jan17-May23 where min comments was 30 in Feb-2017",
       x = "Year",
       y = "Share of comments including the stemmed word") +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  theme_minimal()
play_freqplot

```

